### 2016-09-11 draft/draft.tex
Adds abstract

\begin{abstract}

@@

This project began as an attempt to address this phenomenon of student
disengagement and, over time, developed into a wholly larger
investigation of whether it is possible to utilise blockchain technology
not just to form a network of re-engaged students, but as a tool for the
verification of group-based work at large.\\
The major goals of the project were thus twofold: in a broader sense, to
demonstrate how the properties of a blockchain can be leveraged in a
social, communal context, rather than the financial contexts they are
usually applied to, and more concretely, to create a free, open and
extensible platform for students of all ages to re-engage with their
peers in a productive, educational manner, underpinned by a model of
motivation which rewards collaborative work as a team.

Working from this technological and philosophical objective,
respectively, the following goals were established for the project: -
Create a public Application Programming Interface (henceforth API) to
allow users to interact with a blockchain in a well-defined manner,
independent of a chosen client-side implementation. - Provide an iOS
client-side app for basic task/user/team management to offer a graphical
representation of the API in a format familiar to users. - Establish a
basic deployment of at least 4 distributed validator nodes to implement
a true proof-of-stake consensus
mechanism\cite{BitFuryGroup2015} for the platform.

@@

At the outset of this project, the author intentionally defined the
goals at a level which would be challenging, even possibly unfeasible,
to reach in the time space available, with no other developers to split
workloads with. Considering this context, the project's goals were
largely met, forming a healthy basis for future endeavours of this kind
to build on.\\
The first and most challenging goal was to establish a functioning
public API which would allow individuals to form teams of their own
choosing and register the team's completed tasks on a blockchain. This
was achieved in what the author would classify as a ``naïve''
implementation. Section 6.4 provides details on the author's reasoning
for the term ``naïve''.\\
The second goal of the project was to build a client-side application to
showcase the API's functionality in visual terms. This goal was achieved
at a level satisfactory to the author, considering that the primary
focus of the project lay in establishing the API and the stack of
technologies backing it.\\
The third goal was to deploy a basic network of validator nodes which
would implement a true proof-of-stake consensus algorithm for the
blockchain. This was a surprisingly smooth undertaking due to the high
quality CLIs of Eris, Docker and AWS, allowing a smooth transition from
a single local node to a truly distributed set of validator nodes for
the blockchain.

>>>>

\begin{abstract}
The ability to work proficiently in collaboration with others is highly valued within a large number of social contexts. Yet, a person's ability to do so is scarcely quantifiable in any meaningful way. The goal of this project was therefore to examine the feasibility of constructing a system which can verify and quantify collaborative work. The project was set in the specific context of attempting to solve student disengagement, as the larger concept arose from this concrete problem.

The project attempts to provide a high level of potential for true verification and quantification of collaborative data by utilising a distributed data structure known as a blockchain. Following an analysis of how the proposed system could be structured in terms of interactions between a client the blockchain, an API was constructed to provide as much functionality as was feasible within the time available. Additionally, a simple client-side mobile application was developed to showcase the API's functionality in a concrete manner.

While the project falls short of establishing a manner to truly verify and quantify collaborative work with a distributed blockchain, it demonstrates that such an endeavour is certainly feasible given more time and expertise in the topic area, thus providing a basis for future work to create a \emph{bona fide} system for verification and quantification of team work.
\end{abstract}

@@

This project began as an attempt to address this phenomenon of student
disengagement and, over time, developed into a wholly larger
investigation of whether it is possible to utilise blockchain technology
not just to form a network of re-engaged students, but as a tool for the
verification and quantification of group-based work at large.\\
The major motivations that guided the project were thus twofold: in a broader sense, to
demonstrate how the properties of a blockchain can be leveraged in a
social, communal context, rather than the financial contexts they are
usually applied to, and more concretely, to create a free, open and
extensible platform for students of all ages to re-engage with their
peers in a productive, educational manner, underpinned by a model of
motivation which rewards collaborative work as a team.

Working from this technological and philosophical motivation,
respectively, the following goals were established for the project:\\
- Create a public Application Programming Interface (henceforth API) to allow users to
interact with a blockchain in a well-defined manner, independent of a chosen client-side implementation.\\
- Provide an iOS client-side app for basic task/user/team management to offer a graphical
representation of the API in a format familiar to users.\\

@@

At the outset of this project, the author intentionally defined the
goals at a level which would be challenging, even possibly unfeasible,
to reach in the time space available, with no other developers to split
workloads with. Considering this context, the project's goals were
largely met, forming a healthy basis for future endeavours of this kind
to build on.\\
The first and most challenging goal was to establish a functioning
public API which would allow individuals to form teams of their own
choosing and register the team's completed tasks on a blockchain. This
was achieved in what the author would classify as a ``naïve''
implementation. Section 6.4 provides details on the author's reasoning
for the term ``naïve''.\\
The second goal of the project was to build a client-side application to
showcase the API's functionality in visual terms. This goal was achieved
at a level satisfactory to the author, considering that the primary
focus of the project lay in establishing the API and the stack of
technologies backing it.\\
